---
title: "Analysis Workflow Step 2: Inner Loop Model Selection"
author: "Gaylen Fronk"
format: html
---

## Setup

Load libraries
```{r, message = FALSE}
library(tidyverse)
library(tidymodels)
```

Source functions file
```{r}
source("fun_moodivate.R")
```
This functions file (fun_moodivate.R) contains many functions that are used throughout the Moodivate project analysis scripts. Functions split data, fit and evaluate models, and provide helper functionality for the modeling process. See all annotated code building functions within fun_moodivate.R.

```{r defaults}
#| include: false

knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

## Read in data

Read in results file ("results.csv") created in 01_fit_inner.qmd. This file contains one row per model configuration (unique combination of model tuning parameters and feature set) for each held-out fold. Each row contains the model configuration information (outer split number, inner split number, feature set, hp1 [alpha/mixture], and hp2 [lambda/penalty]). Each row also contains performance metrics for the model fit in the held-in data and evaluated in the indicated validation set (held-out fold from inner loop). 

For RData objects:
```{r}
load("~/Desktop/musc/dahne_lab/moodivate/results_eda_phq_full_feature_set.Rdata")
results_1 <- results
rm(results)
load("~/Desktop/musc/dahne_lab/moodivate/results_nested_eda_phq_wk3.Rdata")

results <- results |> 
  bind_rows(results_1) |> 
  arrange(outer_split_num, inner_split_num)
```


For .csv files:
```{r eval = FALSE}
cv_resample_type <- "nested"

results_files <- str_subset(
  list.files("~/Desktop/musc/dahne_lab/moodivate",
             full.names = TRUE), 
  str_c("results_", cv_resample_type))

no_all <- str_which(results_files, "all", negate = TRUE)
# remove if there is already a results_all file
# to avoid reading in duplicates

results_files <- results_files[no_all]

results <- results_files |> 
  map(\(file) read_csv(file, show_col_types = FALSE)) |> 
  list_rbind() |> 
  arrange(outer_split_num, inner_split_num)

glimpse(results)

results |> 
  write_csv(str_c("~/Desktop/musc/dahne_lab/moodivate/results_",
                  cv_resample_type, "_all.csv"))

#results_all <- results
```

## Process metrics

Check for duplicates
```{r duplicates}
nrow(results)

results <- results |> 
  distinct(outer_split_num, inner_split_num, feature_set, hp1, hp2,
           .keep_all = TRUE)

nrow(results)
```

Checks that breakdowns are as expected. Should be equal numbers of each value.
```{r}
results |> janitor::tabyl(outer_split_num) 
results |> janitor::tabyl(inner_split_num) 
results |> janitor::tabyl(hp1) 
results |> janitor::tabyl(hp2) 
results |> janitor::tabyl(feature_set)
```

## Median metrics across inner folds for model configurations

This process groups by `outer_split_number`, `feature_set`, `hp1`, and `hp2` such that each group contains the 10 inner held-out folds per unique combination of outer split number, feature set, and tuning parameters. The `summarize()` function then averages model performance metrics across the 10 held-out folds (i.e., validation sets). Validation set performance will be used for **model selection** in script 03_fit_eval_outer.qmd. 

```{r}
metrics_avg <- results |> 
  group_by(outer_split_num, feature_set, hp1, hp2) |> 
  summarize(across(c(roc_auc, accuracy,
                     sens, spec, ppv, npv),
                   median),
            n_jobs = n(), .groups = "drop") |> 
  relocate(n_jobs) |> 
  arrange(desc(roc_auc)) |> 
  ungroup()
```

### Review
```{r}
unique(metrics_avg$n_jobs)
```
The `n_jobs` variable should always be 10 jobs (10 inner held-out folds per combination of outer split number, feature set, and tuning parameters). 

Create grouping variables
```{r}
metrics_avg <- metrics_avg |> 
  mutate(week = str_sub(feature_set, start = -3L),
         phq = if_else(str_detect(feature_set, "phq"), "phq", "eda_only"),
         feat_type = str_sub(feature_set, start = 5L, end = -10L))
  
```

**Performance: Overall**

```{r}
metrics_avg |> 
  select(feature_set, hp1, hp2, roc_auc) |> 
  slice(1:50) 

# metrics_avg |> 
#   mutate(feat_cat = if_else(str_detect(feature_set, "phq"),
#                             "eda_and_phq",
#                             "eda_only")) |> 
#   ggplot(aes(x = roc_auc, fill = feat_cat)) +
#   geom_histogram(position = "dodge")

metrics_avg |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc))
```

**Performance Across Individual Feature Sets**
```{r}
metrics_avg |> 
  group_by(feature_set) |> 
  summarize(median_auc = median(roc_auc)) |> 
  arrange(desc(median_auc))
```

**Performance Across Weeks**
```{r}
metrics_avg |> 
  group_by(week) |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc))
```

**Performance Across PHQ Inclusion**
```{r}
metrics_avg |> 
  group_by(phq) |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc))
```

**Performance Across Feature Set Type**
```{r}
metrics_avg |> 
  group_by(feat_type) |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc))
```

Performance of best configurations
```{r}
set.seed(11397)
configs_best <- metrics_avg |> 
  # mutate(feat_cat = if_else(str_detect(feature_set, "phq"),
  #                           "eda_and_phq",
  #                           "eda_only")) |> 
  group_by(outer_split_num) |> 
  # select config w max roc_auc with highest hp1 (closest to lasso)
  # keep remaining ties (i.e., same roc_auc and same hp1)
  slice_max(order_by = tibble(roc_auc, hp1), with_ties = TRUE) |> 
  ungroup() |> 
  group_by(outer_split_num) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup()

configs_best |> 
  select(outer_split_num, feature_set, hp1, hp2, roc_auc) |> 
  arrange(feature_set) |> 
  print(n = Inf)
```

Best configurations "grouped" (to see performance "crossing" of week by PHQ/no)
```{r}
set.seed(11397)
configs_best_grp <- metrics_avg |> 
  group_by(outer_split_num, week, phq) |> 
  # select config w max roc_auc with highest hp1 (closest to lasso)
  # keep remaining ties (i.e., same roc_auc and same hp1)
  slice_max(order_by = tibble(roc_auc, hp1), with_ties = TRUE) |> 
  ungroup() |> 
  group_by(outer_split_num, week, phq) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup()

configs_best_grp |> 
  select(outer_split_num, week, phq, feature_set, roc_auc) |> 
  arrange(week, phq) |> 
  print(n = Inf)

configs_best_grp |> 
  group_by(week, phq) |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc))
```

Save average metrics file
```{r}
metrics_avg |> 
  arrange(outer_split_num, feature_set, hp1, hp2) |> 
  readr::write_csv("~/Desktop/musc/dahne_lab/moodivate/metrics_inner_avg.csv")
```

## Plot tuning parameters

This plot shows performance as a function of alpha/mixture (`hp1`) and lambda/penalty (`hp2`) separately for each `feature_set`. With shuffled data, there is no real pattern of performance as a function of tuning parameters, creating odd-looking output.

With real data, we will confirm that the plot captures a peak (i.e., local maximum) in performance (auROC) before continuing to outer loop model fitting and evaluation. If performance is increasing toward one end of the range for either tuning parameter, we will **NOT** yet proceed to fitting and evaluating models in the outer loop (in 03_fit_eval_outer.qmd). First, we will add model configurations that expand the range, run those additional configurations in the inner loop, and re-evaluate model performance as a function of tuning parameters. 

```{r}
metrics_plot <- results |> 
  # don't group by outer_split_num, otherwise too many data points
  group_by(feature_set, hp1, hp2) |> 
  summarize(across(c(accuracy, roc_auc,
                     sens, spec, ppv, npv),
                   median),
            n_jobs = n(), .groups = "drop") |> 
  relocate(n_jobs) |> 
  arrange(desc(roc_auc)) |> 
  ungroup() 

feature_sets <- unique(metrics_plot$feature_set) 

for (i in feature_sets) {
  
  results_i <- metrics_plot %>% 
    filter(feature_set == i)
  
  plot_title <- stringr::str_c("Plotting glmnet hyperparameters for ", 
                               i, " models")
  
  plot_i <- results_i %>%
    mutate(hp1 = factor(hp1, ordered = TRUE)) %>% 
    ggplot(mapping = aes(x = log(hp2), 
                         y = roc_auc, 
                         group = hp1, 
                         color = hp1)) +
    geom_point(size = 0.1) +
    facet_wrap(vars(hp1)) +
    scale_color_discrete(name = "mixture (alpha)") +
    labs(title = plot_title, x = "penalty (lambda)", y = "auROC")
  
  print(plot_i)
  
}
```

## Plot by feature set

```{r}
metrics_plot <- results |> 
  # don't group by outer_split_num, otherwise too many data points
  group_by(algorithm, feature_set, hp1, hp2) |> 
  summarize(across(c(accuracy, roc_auc,
                     sens, spec, ppv, npv),
                   median),
            n_jobs = n(), .groups = "drop") |> 
  relocate(n_jobs) |> 
  arrange(desc(roc_auc)) |> 
  ungroup() 

metrics_plot <- metrics_plot |> 
  group_by(feature_set) |> 
  summarize(med_roc = median(roc_auc)) |> 
  ungroup()

# larger feature sets
metrics_plot |> 
  ggplot(mapping = aes(x = feature_set,
                       fill = feature_set,
                       y = med_roc)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Performance by Feature Set",
       x = "auROC")

# simpler feature sets

```


```{r}
configs_best |> 
  pull(feature_set) |> 
  janitor::tabyl()

metrics_avg |> 
  filter(feature_set == "total_time") |> 
  pull(roc_auc) |> 
  median()



```

stepwise regression starting total time, see what it wants to add?
non-linear relationships - evan will evaluate linearity of relationships of each variable with outcome
consider other algorithms? quadratic terms?

decision: keep going! find a way to distinguish responders and non-responders!

distribution of BDI outcome by BDI baseline

should BDI baseline interact with other variables?

univariate relationships - check for linearity
correlation table among variables

EDA STEPS
1. overall / responders / non-responders "table" with rows for each variable plus is there a significant relationship
-- group by feature type, separate out by week within each group
-- descriptive stats in each of the columns (overall plus R/NR), plus column with appropriate stat test of difference across groups
-- visually: plot each feature type over time then use loess. one panel overall, second panel colored/grouped by outcome

2. density plots - one panel overall, second panel overlaid plots colored by response category. histograms or bar charts depending on how "discrete" the variable levels are. 4 X 2 where each row is a time point and each column is overall vs by outcome group

3. linearity (EVAN) - smoothed scatterplots

4. correlations among predictors


