---
title: "Analysis Workflow Step 3: Fit & evaluate models in outer loop"
author: "Gaylen Fronk"
format: html
---

## Setup

Load libraries
```{r, message = FALSE}
library(tidyverse)
library(tidymodels)
library(tidyposterior)
```

Source functions file
```{r}
source("fun_moodivate.R")
```
This functions file (fun_moodivate.R) contains many functions that are used throughout the Moodivate project analysis scripts. Functions split data, fit and evaluate models, and provide helper functionality for the modeling process. See all annotated code building functions within fun_moodivate.R.

```{r defaults}
#| include: false

knitr::opts_chunk$set(attr.output='style="max-height: 500px;"')

options(tibble.width = Inf)
options(tibble.print_max = Inf)
```

## Read in average metrics

Metrics averaged across inner folds (10 folds per average) for each unique model configuration (combination of feature set and two hyperparameters) for each outer fold (30 splits).

```{r}
metrics_avg <- read_csv(
  "~/Desktop/musc/dahne_lab/moodivate/metrics_inner_avg.csv", 
  show_col_types = FALSE)

glimpse(metrics_avg)
```

### Select best configurations

We select the best model configuration for each outer fold for each combination of week and PHQ vs. no-PHQ. Specifically, these are the model configurations that produce the highest average performance across *validation sets* (held-out inner folds) in each outer fold for each combination. 

In the case of ties (i.e., equal AUC across multiple configurations in an outer split/week/PHQ), we:

1. Choose the configuration(s) with the lowest alpha (`hp1`) to prefer a parsimonious model.

2. Randomly select among remaining tied configurations (i.e., same AUC and same lowest alpha hyperparameter).

Best configurations "grouped" (to see performance "crossing" of week by PHQ/no)
```{r}
set.seed(11397)
configs_best_grp <- metrics_avg |> 
  group_by(outer_split_num, week, phq) |> 
  # select config w max roc_auc with highest hp1 (closest to lasso)
  # keep remaining ties (i.e., same roc_auc and same hp1)
  slice_max(order_by = tibble(roc_auc, hp1), with_ties = TRUE) |> 
  ungroup() |> 
  group_by(outer_split_num, week, phq) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup()

configs_best_grp |> 
  select(outer_split_num, week, phq, feature_set, roc_auc) |> 
  arrange(week, phq) |> 
  print(n = Inf)

configs_best_grp |> 
  group_by(week, phq) |> 
  summarize(median_auc = median(roc_auc),
            min_auc = min(roc_auc),
            max_auc = max(roc_auc),
            mean_auc = mean(roc_auc))
```

Looking at the mean and median performance of the best selected models in the inner loop, we see that there is relatively normal distribution of auROC values (mean and median values are similar). 

Most selected feature types
```{r}
configs_best_grp |> 
  filter(phq == "phq") |> 
  pull(feat_type) |> 
  janitor::tabyl() |> 
  arrange(desc(n))

configs_best_grp |> 
  filter(phq == "eda_only") |> 
  pull(feat_type) |> 
  janitor::tabyl() |> 
  arrange(desc(n))

configs_best_grp |> 
  filter(week == "wk2") |> 
  pull(feat_type) |> 
  janitor::tabyl() |> 
  arrange(desc(n))

configs_best_grp |> 
  filter(week == "wk3") |> 
  pull(feat_type) |> 
  janitor::tabyl() |> 
  arrange(desc(n))

configs_best_grp |> 
  filter(week == "wk4") |> 
  pull(feat_type) |> 
  janitor::tabyl() |> 
  arrange(desc(n))

```


## Read in data

```{r}
d <- read_csv("~/Desktop/musc/dahne_lab/moodivate/data_clean.csv", 
              show_col_types = FALSE) |> 
  glimpse()
```

## Prepare data

Following the same process as in script 01_fit_inner.qmd, we define our outcome variable (y_col_name) as `phq_outcome_cat`, which will be renamed as `y` to facilitate using cross-study functions and code. The two levels of the outcome variable (non-responder and responder) are set to have non-responder as the positive (event) level, as our goal is to identify non-responders to the Moodivate DMHI who should be stepped up to a higher level of care.

```{r}
y_col_name <- "phq9_outcome_cat"
y_level_pos <- "non_responder"
y_level_neg <- "responder"
y_baseline <- "phq9_baseline"
```

### Class variables & set factor levels

```{r}
d <- d |> 
  # rename outcome to y
  rename(y = !!y_col_name) |> 
  mutate(y = case_when(
    y == "NonResponder" ~ "non_responder",
    y == "Responder" ~ "responder",
    TRUE ~ NA_character_)) %>% 
  # y as a factor with two levels, positive level first
  mutate(y = factor(y, levels = c(!!y_level_pos,
                                  !!y_level_neg))) |> 
  # rename baseline to y_base
  rename(y_base = !!y_baseline) |> 
  # remove other outcome & baseline variables
  select(-contains("outcome"), -contains("baseline")) |> 
  # remove variables not included in ANY feature sets
  select(record_id, y_base, y,
         starts_with("session_count_w"),
         average_session_time_wk3,
         starts_with("total_time_w"),
         starts_with("schedule_activity_w"),
         starts_with("scheduled_activities_w"),
         completed_activities_wk1, completed_activities_wk3, 
         completed_activities_wk4, mood_days_wk1,
         add_goal_wk1, add_goal_chg_wk1_wk3, add_goal_chg_wk1_wk4,
         starts_with("add_goal_chg_from_avg"),
         badges_earned_wk1, badges_earned_wk3,
         badges_earned_chg_wk1_wk4, badges_earned_chg_from_avg_wk4,
         total_time_chg_wk1_wk3, total_time_chg_wk1_wk4,
         starts_with("total_time_chg_from_avg"),
         schedule_activity_chg_from_prev_wk3,
         phq8_comp_chg_wk1_wk4,
         starts_with("phq9_change")) |> 
  # move bdi_baseline/phq_baseline to be first variable in dataset
  #for penalty.factor
  relocate(y_base, y, everything()) 
```

## Fit outer loop models using best selected configurations

We follow the same model fitting process as in 01_fit_inner.qmd. The difference is that we are now fitting only the best selected model configuration in each set of held-in outer folds, and predicting into the corresponding held-out fold. 

Note that data are divided identically using the same seed.

Models are fit using `fit_predict_eval()` from fun_moodivate.R - this function fits the model and makes predictions. We map over each held-out outer fold to produce 180 *test set* estimates of model performance.

```{r eval_outer_folds}
# set up a temporary id number to track participants across fits
record_ids <- d$record_id
d <- d |> 
  mutate(id_obs = record_ids)
rm(record_ids)

# set up cross-validation (identical splits as previous scripts)
cv_resample_type <- "nested"
cv_outer_resample <- "3_x_10"
cv_inner_resample <- "1_x_10"
seed_splits <- 52592

splits <- d |> 
  make_splits(cv_resample_type, cv_resample, cv_outer_resample,
              cv_inner_resample, the_seed = seed_splits,
              strata = "y")

# map function fit_predict_eval() across each row of configs_best
all <- 1:nrow(configs_best_grp) |> 
  map(\(config_num) fit_predict_eval(config_num, splits, configs_best_grp))  

metrics_out <- all |> 
  map(\(l) pluck(l, "metrics_out")) |> 
  list_rbind() |> 
  write_rds("~/Desktop/musc/dahne_lab/moodivate/outer_metrics.rds")

preds_out <- all |> 
  map(\(l) pluck(l, "probs_out")) |> 
  list_rbind() |> 
  write_rds("~/Desktop/musc/dahne_lab/moodivate/outer_preds.rds")


```

## Evaluate performance

### Inner Loop AUC

Best model configurations were selected using the median auROCs across 10 inner folds. 90 (3x10 for each of 3 feature sets) models were selected. These performance estimates are from the inner folds (i.e., validation sets) and were used *only* for selection and not for evaluation.

```{r}
metrics_out |> 
  group_by(week, phq) |> 
  summarize(median(roc_auc_in), mean(roc_auc_in), 
            min(roc_auc_in), max(roc_auc_in), sd(roc_auc_in)) |> 
  glimpse()
```

### Outer AUC

Best model configurations were evaluated using the auROCs from the 90 (3x10 for each of 3 feature sets) outer folds (i.e., test sets). These performance metrics were used *only* for evaluation and not for selection. 

Outer overall
```{r metrics_out}
metrics_out |> 
  group_by(phq, week) |> 
  summarize(min = min(roc_auc), 
            iqr25 = quantile(roc_auc, probs = 0.25),
            median = median(roc_auc), 
            iqr75 = quantile(roc_auc, probs = 0.75),
            max = max(roc_auc)) 
```

Side by side of inner & outer median AUCs
```{r}
metrics_out |> 
  group_by(week, phq) |> 
  summarize(median(roc_auc), median(roc_auc_in),
            mean(roc_auc), mean(roc_auc_in))
```

Plot outer fold auROCs
```{r plot_outer}
metrics_out |> 
  ggplot(aes(x = roc_auc)) +
  geom_histogram(bins = 10)  

```

### Full Outer Metrics

```{r}
metrics_out |> 
  group_by(phq, week) |> 
  summarize(median(roc_auc),
            median(sens),
            median(spec),
            median(ppv),
            median(npv),
            median(accuracy))
```


## ROC curves

Make configuration-specific preds_out datasets
```{r}
preds_out_eda2 <- preds_out |> 
  filter(str_detect(feature_set, "_wk2") & !str_detect(feature_set, "phq"))

preds_out_eda3 <- preds_out |> 
  filter(str_detect(feature_set, "_wk3") & !str_detect(feature_set, "phq"))

preds_out_eda4 <- preds_out |> 
  filter(str_detect(feature_set, "_wk4") & !str_detect(feature_set, "phq"))

preds_out_phq2 <- preds_out |> 
  filter(str_detect(feature_set, "_wk2") & str_detect(feature_set, "phq"))

preds_out_phq3 <- preds_out |> 
  filter(str_detect(feature_set, "_wk3") & str_detect(feature_set, "phq"))

preds_out_phq4 <- preds_out |> 
  filter(str_detect(feature_set, "_wk4") & str_detect(feature_set, "phq"))
```


```{r roc_info_12}
# week 2, eda only
roc_data_eda2 <- preds_out_eda2 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_eda2 <- roc_data_eda2 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 

# week 2, eda & phq
roc_data_phq2 <- preds_out_phq2 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_phq2 <- roc_data_phq2 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 

# week 3, eda only
roc_data_eda3 <- preds_out_eda3 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_eda3 <- roc_data_eda3 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 

# week 3, eda & phq
roc_data_phq3 <- preds_out_phq3 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_phq3 <- roc_data_phq3 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 

# week 4, eda only
roc_data_eda4 <- preds_out_eda4 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_eda4 <- roc_data_eda4 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 

# week 4, eda & phq
roc_data_phq4 <- preds_out_phq4 |> 
  roc_curve(prob_raw, truth = label)

fig_roc_phq4 <- roc_data_phq4 %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = .threshold)) +
  geom_path(linewidth = 2) +
  geom_abline(lty = 3) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  labs(x = "",
       y = "",
       color = "Threshold") +
  scale_x_continuous(breaks = seq(0,1,.25),
                     labels = sprintf("%.2f", seq(1,0,-.25))) +
  scale_color_gradient(low="blue", high="red",
                       limits = c(0, 1)) 
```

Combine into single figure
```{r}
library(patchwork)

patchwork <- ( fig_roc_eda2 + fig_roc_phq2 ) /
  ( fig_roc_eda3 + fig_roc_phq3 ) /
  ( fig_roc_eda4 + fig_roc_phq4 )

patchwork +
  plot_layout(guides = "collect") 
```

## Confusion matrices 

### Confusion matrix using .5 threshold
```{r default_cm}
# engagement-only, through W2
(cm <- preds_out_eda2 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement-only, through W3
(cm <- preds_out_eda3 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement-only, through W4
(cm <- preds_out_eda4 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement + clinical, through W2
(cm <- preds_out_phq2 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement + clinical, through W3
(cm <- preds_out_phq3 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement + clinical, through W4
(cm <- preds_out_phq4 |> 
   mutate(estimate = if_else(prob_raw > .5, "non_responder", "responder"),
          estimate = factor(estimate, 
                            levels = c("non_responder", "responder"))) |> 
   conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

```

### Confusion matrix at optimal cut-point (based on Youdens J index)

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1444894/
https://pubmed.ncbi.nlm.nih.gov/15405679/

```{r youden_cm}
# engagement-only, through W2
j_thres_roc <- roc_data_eda2 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_eda2 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement-only, through W3
j_thres_roc <- roc_data_eda3 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_eda3 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement-only, through W4
j_thres_roc <- roc_data_eda4 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_eda4 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement+clinical, through W2
j_thres_roc <- roc_data_phq2 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_phq2 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement+clinical, through W3
j_thres_roc <- roc_data_phq3 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_phq3 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()

# engagement+clinical, through W4
j_thres_roc <- roc_data_phq4 |> 
  mutate(j = sensitivity + specificity - 1) |> 
  slice_max(j) |> 
  print() |> 
  pull(.threshold)

(cm <- preds_out_phq4 |> 
    mutate(estimate = if_else(prob_raw > j_thres_roc, "non_responder", "responder"),
           estimate = factor(estimate, 
                             levels = c("non_responder", "responder"))) |> 
    conf_mat(truth = label, estimate = estimate))

cm %>% 
  autoplot() +
  theme(axis.text = element_text(size = rel(1.50)), 
        axis.title = element_text(size = rel(1.75)))

cm %>% summary()
```

## Posterior probability for formal model comparisons

Make context-specific tibbles
```{r}
auc_eda2 <- metrics_out |> 
  filter(week == "wk2" & phq == "eda_only") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_eda3 <- metrics_out |> 
  filter(week == "wk3" & phq == "eda_only") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_eda4 <- metrics_out |> 
  filter(week == "wk4" & phq == "eda_only") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_phq2 <- metrics_out |> 
  filter(week == "wk2" & phq == "phq") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_phq3 <- metrics_out |> 
  filter(week == "wk3" & phq == "phq") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)

auc_phq4 <- metrics_out |> 
  filter(week == "wk4" & phq == "phq") |> 
  arrange(outer_split_num) |> 
  mutate(repeat_num = rep(str_c("repeat", 1:3), each = 10),
         fold_num = rep(str_c("fold", 1:10),3)) |>   # assumes 3x10 fold
  select(repeat_num, fold_num, roc_auc)
```

Combine
```{r}
auc <- auc_eda2 |> 
  rename(eng_wk2 = roc_auc) |> 
  mutate(eng_wk3 = auc_eda3$roc_auc,
         eng_wk4 = auc_eda4$roc_auc,
         phq_wk2 = auc_phq2$roc_auc,
         phq_wk3 = auc_phq3$roc_auc,
         phq_wk4 = auc_phq4$roc_auc) |> 
  glimpse()
```

### Generate posterior probability distributions

```{r bayes}
# from ?perf_mod()
# Repeated CV (id [k] = repeat, id2 [j] = fold within repeat)
# with a common variance:  statistic ~ model + (model | id/id2)
# NOTE: that id/id2 format follows stanarm/glmer formatting rather than tidyposterior recommendations
set.seed(101)
pp <- auc |> 
  rename(id = repeat_num,
         id2 = fold_num) |> 
  perf_mod(formula = statistic ~ model + (1 | id/id2),
           # prior_intercept = rstanarm::student_t(autoscale = TRUE),
           # prior = rstanarm::student_t(autoscale = TRUE),
           transform = tidyposterior::logit_trans,  # for skewed & bounded AUC
           iter = 10000, chains = 4,  
           adapt_delta = .999,
           hetero_var = TRUE,
           family = gaussian
  )  
```
in order to compare performance across model contexts - used Bayesian model to calculate probabilities that average performance across models differ, and evaluated those. also include sentence "these are not p-values - we want them to be away from 0.5, closer to 1 - suggest increased performance for second feature set relative to the first"

"We fit a Bayesian linear mixed-effects model using the collection of 180 estimated test set AUCs (6 feature sets X 10 folds X 3 repeats) to compare performance across feature sets. Specifically, from the model we are able to estimate the probability that 

Prob (Average AUCi > Average AUCi') where i and i' index distinct feature sets (See Technical Supplement). 

RESULTS: 
We did this to evaluate the improvement in performance / value added with respect to classification performance... 
```{r}
rstanarm::prior_summary(pp$stan)
```

```{r}
summary(pp$stan)
```

### Model posterier CIs

```{r}
pp_tidy <- pp |> 
  tidy(seed = 123)

q = c(.025, .5, .975)
pp_tidy |> 
  group_by(model) |> 
  summarize(median = quantile(posterior, probs = q[2]),
            lower = quantile(posterior, probs = q[1]), 
            upper = quantile(posterior, probs = q[3])) |> 
  mutate(model = factor(model, levels = c("eng_wk2", "eng_wk3", "eng_wk4",
                                          "phq_wk2", "phq_wk3", "phq_wk4"),
                        labels = c("Engagement Only (Week 2)", 
                                   "Engagement Only (Week 3)", 
                                   "Engagement Only (Week 4)",
                                   "Engagement + Clinical (Week 2)",
                                   "Engagement + Clinical (Week 3)",
                                   "Engagement + Clinical (Week 4)")),
         y = 1000) |> 
  arrange(model)

```


### Model contrasts

Compare within times by data type (e.g., engagement wk2 vs. eng + clinical wk2) and within data type by time (e.g., engagement wk2 vs. engagement wk3)

Use median change in auROC & CIs from this table
```{r}
pp_contrasts <- contrast_models(pp,
                                list("eng_wk3", "eng_wk4", "phq_wk2",
                                     "eng_wk4", "phq_wk3", "phq_wk4",
                                     "phq_wk3", "phq_wk4", "phq_wk4"),
                                list("eng_wk2", "eng_wk2", "eng_wk2", 
                                     "eng_wk3", "eng_wk3", "eng_wk4",
                                     "phq_wk2", "phq_wk2", "phq_wk3"))
summary(pp_contrasts, size = .01, prob = 0.95)
pp_contrasts |> autoplot(size = .01)
```

Contrasts against 0 rather than using ROPE
```{r}
# engagement across time contrasts
pp_contrasts |> 
  filter(contrast == "eng_wk3 vs. eng_wk2") |> 
  mutate(eng3_gt_eng2 = if_else(difference > 0, 1, 0)) |>
  pull(eng3_gt_eng2) |> 
  mean() # probability of 0.366 that wk3 > wk2

pp_contrasts |> 
  filter(contrast == "eng_wk4 vs. eng_wk2") |> 
  mutate(eng4_gt_eng2 = if_else(difference > 0, 1, 0)) |>
  pull(eng4_gt_eng2) |> 
  mean() # probability of 0.326 that wk4 > wk2

pp_contrasts |> 
  filter(contrast == "eng_wk4 vs. eng_wk3") |> 
  mutate(eng4_gt_eng3 = if_else(difference > 0, 1, 0)) |>
  pull(eng4_gt_eng3) |> 
  mean() # probability of 0.456 that wk4 > wk3

# engagement + clinical across time contrasts
pp_contrasts |> 
  filter(contrast == "phq_wk3 vs. phq_wk2") |> 
  mutate(phq3_gt_phq2 = if_else(difference > 0, 1, 0)) |>
  pull(phq3_gt_phq2) |> 
  mean() # probability of 0.362 that wk3 > wk2

pp_contrasts |> 
  filter(contrast == "phq_wk4 vs. phq_wk2") |> 
  mutate(phq4_gt_phq2 = if_else(difference > 0, 1, 0)) |>
  pull(phq4_gt_phq2) |> 
  mean() # probability of 0.970 that wk4 > wk2

pp_contrasts |> 
  filter(contrast == "phq_wk4 vs. phq_wk3") |> 
  mutate(phq4_gt_phq3 = if_else(difference > 0, 1, 0)) |>
  pull(phq4_gt_phq3) |> 
  mean() # probability of 0.992 that wk4 > wk3

# addition of clinical data contrasts
pp_contrasts |> 
  filter(contrast == "phq_wk2 vs. eng_wk2") |> 
  mutate(phq2_gt_eng2 = if_else(difference > 0, 1, 0)) |>
  pull(phq2_gt_eng2) |> 
  mean() # probability of 1.000 that adding clinical data improves performance

pp_contrasts |> 
  filter(contrast == "phq_wk3 vs. eng_wk3") |> 
  mutate(phq3_gt_eng3 = if_else(difference > 0, 1, 0)) |>
  pull(phq3_gt_eng3) |> 
  mean() # probability of 1.000 that adding clinical data improves performance

pp_contrasts |> 
  filter(contrast == "phq_wk4 vs. eng_wk4") |> 
  mutate(phq4_gt_eng4 = if_else(difference > 0, 1, 0)) |>
  pull(phq4_gt_eng4) |> 
  mean() # probability of 1.000 that adding clinical data improves performance


```

### Figure: Model posteriors & CIs

```{r}

pp_tidy_fig <- pp_tidy |> 
  mutate(model = factor(model, 
                        levels = c("eng_wk2", "eng_wk3", 
                                   "eng_wk4", "phq_wk2", 
                                   "phq_wk3", "phq_wk4"))) |> 
  mutate(data_type = if_else(str_detect(model, "phq"), "Clinical Data Added",
                             "Engagement Only"),
         week = str_sub(model, start = -1L, end = -1L)) |> 
  mutate(week = str_c("Week ", week),
         data_type = fct_relevel(data_type, 
                                 "Engagement Only", "Clinical Data Added"))

ci <- pp_tidy_fig |> 
  summary() |> 
  mutate(model = factor(model, 
                        levels = c("eng_wk2", "eng_wk3", 
                                   "eng_wk4", "phq_wk2", 
                                   "phq_wk3", "phq_wk4")),
         y = 1000)  |> 
  mutate(data_type = if_else(str_detect(model, "phq"), "Clinical Data Added",
                             "Engagement Only"),
         week = str_sub(model, start = -1L, end = -1L)) |> 
  mutate(week = str_c("Week ", week),
         data_type = fct_relevel(data_type, 
                                 "Engagement Only", "Clinical Data Added"))

theme_set(theme_classic())
pp_tidy_fig |> 
  ggplot() + 
  geom_histogram(aes(x = posterior, fill = data_type), 
                 color = "black", alpha = .4, 
                 bins = 30) +
  geom_segment(mapping = aes(y = y+250, yend = y+50, x = mean, xend = mean,
                             color = data_type),
               data = ci) +
  geom_segment(mapping = aes(y = y+150, yend = y+150, x = lower, xend = upper, 
                             color = data_type),
               data = ci) +
  facet_wrap(~week, ncol = 1) +
  #facet_grid(rows = vars(week), cols = vars(data_type)) +
  scale_y_continuous("Posterior Probability", breaks = c(0, 500, 1000)) +
  # ylab("Posterior Probability Density") +
  labs(x = "Area Under ROC Curve",
       color = "Data Type",
       fill = "Data Type") +
  theme(legend.position = "bottom")

# simplified figure for poster
pp_tidy_fig |> 
  ggplot() +
  geom_point(mapping = aes(y = 10, x = mean,
                           color = data_type),
             size = 3,
             data = ci) +
  # geom_segment(mapping = aes(y = y+250, yend = y+50, x = mean, xend = mean,
  #                            color = data_type),
  #              data = ci) +
  geom_segment(mapping = aes(y = 10, yend = 10, x = lower, xend = upper, 
                             color = data_type),
               data = ci) +
  facet_wrap(~week, ncol = 1) +
  #facet_grid(rows = vars(week), cols = vars(data_type)) +
  scale_y_continuous(breaks = c(0, 500, 1000)) +
  # ylab("Posterior Probability Density") +
  labs(x = "Area Under ROC Curve",
       y = "",
       color = "Data Type",
       title = "Performance Across Model Contexts") +
  theme(legend.position = "bottom")

```
