---
title: "Analysis Workflow Step 4: Select & fit final model"
author: "Gaylen Fronk"
format: html
---

## Setup

Load libraries
```{r, message = FALSE}
library(glmnet)
library(tidyverse)
library(tidymodels)
library(probably)
```

Source functions file
```{r}
source("fun_moodivate.R")
```
This functions file (fun_moodivate.R) contains many functions that are used throughout the Moodivate project analysis scripts. Functions split data, fit and evaluate models, and provide helper functionality for the modeling process. See all code building functions within fun_moodivate.R. 

## Read in data

```{r}
d <- read_csv("~/Desktop/musc/dahne_lab/moodivate/data_clean.csv", 
              show_col_types = FALSE) |> 
  glimpse()
```

## Prepare data

We prepare our data in the same way as all previous scripts.

### Set up outcome variable levels

```{r}
y_col_name <- "phq9_outcome_cat"
y_level_pos <- "non_responder"
y_level_neg <- "responder"
y_baseline <- "phq9_baseline"
```

### Class variables & set factor levels

```{r}
d <- d |> 
  # rename outcome to y
  rename(y = !!y_col_name) |> 
  mutate(y = case_when(
    y == "NonResponder" ~ "non_responder",
    y == "Responder" ~ "responder",
    TRUE ~ NA_character_)) %>% 
  # y as a factor with two levels, positive level first
  mutate(y = factor(y, levels = c(!!y_level_pos,
                                  !!y_level_neg))) |> 
  # rename baseline to y_base
  rename(y_base = !!y_baseline) |> 
  # remove other outcome & baseline variables
  select(-contains("outcome"), -contains("baseline")) |> 
  # remove variables not included in ANY feature sets
  select(record_id, y_base, y,
         starts_with("session_count_w"),
         average_session_time_wk3,
         starts_with("total_time_w"),
         starts_with("schedule_activity_w"),
         starts_with("scheduled_activities_w"),
         completed_activities_wk1, completed_activities_wk3, 
         completed_activities_wk4, mood_days_wk1,
         add_goal_wk1, add_goal_chg_wk1_wk3, add_goal_chg_wk1_wk4,
         starts_with("add_goal_chg_from_avg"),
         badges_earned_wk1, badges_earned_wk3,
         badges_earned_chg_wk1_wk4, badges_earned_chg_from_avg_wk4,
         total_time_chg_wk1_wk3, total_time_chg_wk1_wk4,
         starts_with("total_time_chg_from_avg"),
         schedule_activity_chg_from_prev_wk3,
         phq8_comp_chg_wk1_wk4,
         starts_with("phq9_change")) |> 
  # move bdi_baseline/phq_baseline to be first variable in dataset
  #for penalty.factor
  relocate(y_base, y, everything()) 
```

## Divide data

### Set cross-validation parameters

Following nested cross-validation conducted in scripts 01-03, the final step is to fit and select models using the *inner loop CV* but in our *entire dataset*. Consequently, we use one repeat of 10-fold CV (using a new seed). Performance metrics from this round of CV will **not** be used for model evaluation; they will only be used for selecting a final model configuration. 

```{r}
cv_resample_type <- "kfold"
cv_resample <- "1_x_10"
seed_splits <- 111594
```

### Make splits 

Divide data using `make_splits()` function (from fun_moodivate.R). We are stratifying by the outcome variable `y` to ensure equal distribution of outcome classes across all inner and outer folds. 
```{r}
splits <- d |> 
  make_splits(cv_resample_type, cv_resample, cv_outer_resample,
              cv_inner_resample, the_seed = seed_splits,
              strata = "y")
```

## Set up model configurations

Possible model configurations are defined identically to previous scripts 01-03.

```{r}
algorithm <- "glmnet"
ml_mode <- "classification"

# alpha (mixture)
hp1_glmnet <- c(0, seq(.1, 1, length.out = 10)) 

# lambda (penalty)
hp2_glmnet_min <- -5 # min for penalty grid - will be passed into exp(seq(min, max, length.out = out))
hp2_glmnet_max <- 5 # max for penalty grid
hp2_glmnet_out <- 200 # length of penalty grid
```

## Make configurations tibble

This is a grid expansion of the splits, hyperparameters, and feature sets. Each row in the tibble will serve as a model configuration that can then be fit below. This tibble will also be used to connect results to model configurations.

### Extract CV parameters from strings

```{r}
n_repeats <- as.numeric(str_remove(cv_resample,
                                   "_x_\\d{1,2}"))
n_folds <- as.numeric(str_remove(cv_resample,
                                 "\\d{1,3}_x_"))
split_num <- 1:(n_repeats * n_folds)

```

### Make configurations grid

```{r}
configs <- expand_grid(split_num = split_num,
                       feature_set = c(#"eda_chg_thru_wk2",
                         # eng only, through wk2
                         "eda_raw_thru_wk2",
                         "eda_actions_thru_wk2",
                         "eda_usage_thru_wk2",
                         "eda_max_thru_wk2",
                         # eng + clin, through wk2
                         "eda_chg_phq_thru_wk2",
                         "eda_raw_phq_thru_wk2",
                         "eda_actions_phq_thru_wk2",
                         "eda_usage_phq_thru_wk2",
                         "eda_max_phq_thru_wk2",
                         # eng + clin, through wk3
                         "eda_chg_phq_thru_wk3",
                         "eda_raw_phq_thru_wk3",
                         "eda_actions_phq_thru_wk3",
                         "eda_usage_phq_thru_wk3",
                         "eda_max_phq_thru_wk3",
                         # eng + clin, through wk4
                         "eda_chg_phq_thru_wk4",
                         "eda_raw_phq_thru_wk4",
                         "eda_actions_phq_thru_wk4",
                         "eda_usage_phq_thru_wk4",
                         "eda_max_phq_thru_wk4",
                         # eng only, through wk3
                         "eda_chg_thru_wk3",
                         "eda_raw_thru_wk3",
                         "eda_actions_thru_wk3",
                         "eda_usage_thru_wk3",
                         "eda_max_thru_wk3",
                         # eng only, through wk4
                         "eda_chg_thru_wk4",
                         "eda_raw_thru_wk4",
                         "eda_actions_thru_wk4",
                         "eda_usage_thru_wk4",
                         "eda_max_thru_wk4"
                       ),
                       hp1 = hp1_glmnet,
                       hp2 = NA_integer_) |> 
  tibble::rownames_to_column("config_num") |> 
  mutate(config_num = as.numeric(config_num))

glimpse(configs)
```

Feature sets are specific combinations of features (data type X weeks included X specific sets of engagement features). 

Note that hp2 (lambda/penalty) is listed as NA because each configuration will `tune()` across the 100 values set using `hp2_glmnet_min`, `hp2_glmnet_max`, and `hp2_glmnet_out` (length). 

## Fit models

As in previous scripts, we set up a wrapper function to `map()` over every model configuration (i.e., every row in the configs tibble). For each model configuration, we:

1. Filter down to only that configuration's row in the model configurations tibble.

2. Build a recipe using the custom `build_recipe()` function (in fun_moodivate.R). 

3. Define a vector of penalty weights, which will apply equal penalty weighting to all variables except `bdi_baseline`, which will have a penalty weight of 0 and consequently will be included in all models. 

4. Fit model, and get model performance metrics using our custom `tune_model()` from the fun_moodivate.R script. This function performs model tuning for the model configuration (defined by `feature_set`, `hp1`, and combination of inner and outer folds) across our range of values of `hp2`. 

5. Append model performance metrics to the configs tibble in a new `results` tibble.

```{r}
fit_eval <- function(config_current, configs, d, splits) {
  
  # filter single config row from configs
  config <- configs |> 
    filter(config_num == config_current)
  
  # build recipe
  rec <- build_recipe(d = d, config = config)
  
  # fit model & get predictions and model metrics
  results <- tune_model(config = config,
                        rec = rec, 
                        splits = splits, 
                        ml_mode = ml_mode, 
                        cv_resample_type = cv_resample_type,
                        hp2_glmnet_min = hp2_glmnet_min, 
                        hp2_glmnet_max = hp2_glmnet_max, 
                        hp2_glmnet_out = hp2_glmnet_out,
                        y_level_pos = y_level_pos)
  
  return(results)
}

```

### Fit models across all configurations

```{r}
tictoc::tic()
if (file.exists(str_c("~/Desktop/musc/dahne_lab/moodivate/results_",
                      cv_resample_type, ".csv"))) {
  results <- read_csv(str_c("~/Desktop/musc/dahne_lab/moodivate/results_",
                            cv_resample_type, ".csv"),
                      show_col_types = F)
} else {
  results <- 1:max(configs$config_num) |> 
    map(\(config_current) fit_eval(config_current, configs, 
                                   d, splits)) |> 
    list_rbind() %>% 
    mutate(new_config_num = 1:nrow(.))
}
tictoc::toc()

```

### Glimpse results

This results file contains the information from the configuration grid, with model performance metrics appended to each row (i.e., model configuration). The grid has now been expanded to include each individual value for `hp2` (lambda/penalty) that was considered within `tune_models()`. 

```{r}
glimpse(results)
```

Save results
```{r}
results |> 
  write_csv(str_c(
    "~/Desktop/musc/dahne_lab/moodivate/results_",
    cv_resample_type, ".csv"))
```

## Select final model configurations

We now use average performance across the 10 held-out folds to select the best model configuration **per model context**. As a reminder, performance metrics are being used *only* for selection and *not* for model evaluation. Evaluation was completed in the outer loop of nested cross-validation.

```{r}
metrics_avg <- results |> 
  group_by(feature_set, hp1, hp2) |> 
  summarize(across(c(accuracy, roc_auc,
                     sens, spec, ppv, npv),
                   median),
            n_jobs = n(), .groups = "drop") |> 
  relocate(n_jobs) |> 
  arrange(desc(roc_auc)) |> 
  ungroup()

glimpse(metrics_avg)
```

Select best model configurations

```{r}
set.seed(51189)

best_config_eda2 <- metrics_avg |> 
  filter(!str_detect(feature_set, "phq") & str_detect(feature_set, "wk2")) |> 
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()

best_config_eda3 <- metrics_avg |> 
  filter(!str_detect(feature_set, "phq") & str_detect(feature_set, "wk3")) |> 
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()

best_config_eda4 <- metrics_avg |> 
  filter(!str_detect(feature_set, "phq") & str_detect(feature_set, "wk4") & !str_detect(feature_set, "max")) |>
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()

best_config_phq2 <- metrics_avg |> 
  filter(str_detect(feature_set, "phq") & str_detect(feature_set, "wk2")) |> 
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()

best_config_phq3 <- metrics_avg |> 
  filter(str_detect(feature_set, "phq") & str_detect(feature_set, "wk3")) |> 
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()

best_config_phq4 <- metrics_avg |> 
  filter(str_detect(feature_set, "phq") & str_detect(feature_set, "wk4")) |> 
  slice_max(roc_auc, with_ties = TRUE) |> 
  # among remaining ties, randomly select single config 
  slice_sample(n = 1) |> 
  ungroup() |> 
  print()
```

Save out best configurations

```{r}
best_configs <- best_config_eda2 |> 
  bind_rows(best_config_eda3) |> 
  bind_rows(best_config_eda4) |> 
  bind_rows(best_config_phq2) |> 
  bind_rows(best_config_phq3) |> 
  bind_rows(best_config_phq4) |> 
  write_csv(str_c(
    "~/Desktop/musc/dahne_lab/moodivate/best_configs.csv"))

```

## Fit final models

Ultimately, we will fit only one final model per model context using the best configuration *selected* above. This will be the model that gets deployed going forward in new studies. Researchers will need to decide which context (combination of data type[s] and weeks included) gives them the best trade-off of performance, burden of data collection, and time before treatment re-assignment.

### Fit final model: Engagement only, through Week 2

```{r}
rec <- build_recipe(d = d, config = best_config_eda2)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_eda2 <- fit_best_model(best_model = best_config_eda2, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_eda2 <- tidy(model_best_full_eda2)

model_tidy_eda2 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_eda2_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_eda2 <- model_tidy_eda2 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_eda2, digits = 6)
```

So, we see that:

People who spend more time in the app in Weeks 1 & 2 (`total_time_wk*` features) are *less* likely to be non-responders (i.e., are more likely to respond). 

People who have more discrete app sessions in Weeks 1 & 2 (`session_count_wk*` features) are *less* likely to be non-responders (i.e., are more likely to respond).

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

**Key Takeaways**: Engaging more, defined as overall time spent in the app and number of discrete sessions, makes you more likely to respond to treatment. More severe depression at baseline increases the likelihood of responding to treatment. 

Get normalization parameters
```{r}
norm_params_eda2 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_eda2 <- norm_params_eda2 |> 
  filter(terms %in% retained_vars_eda2$term)

# pivot wider
norm_params_retained_eda2 <- norm_params_retained_eda2 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_eda2, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```


### Fit final model: Engagement only, through Week 3

```{r}
rec <- build_recipe(d = d, config = best_config_eda3)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_eda3 <- fit_best_model(best_model = best_config_eda3, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_eda3 <- tidy(model_best_full_eda3)

model_tidy_eda3 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_eda3_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_eda3 <- model_tidy_eda3 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_eda3, digits = 6)
```

So, we see that:
change goes up = w3 > w1 = more in the later week = # of [feature] is increasing
positive estimate = as change goes up, likelihood of non-response goes up = as #/use of [feature] increases, less likely to respond

People whose number of goals added increases over time (i.e., number of goals added in Week 3 is higher than number of goals added in Week 1) are *more* likely to be non-responders (i.e., are less likely to respond). 

People whose time spent in the app increases over time (i.e., time spent in the app in Week 3 is higher than time spent in the app in Week 1 or across the average of Weeks 1 & 2) are *more* likely to be non-responders (i.e., are less likely to respond).

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

**Key Takeaways**: Individuals whose engagement (based on number of goals added and time spent in-app) increases are *less* likely to respond; however, when looking at raw values, the Week 1 values are *higher* among responders, but the Week 3 values are *the same* across responders and non-responders. This suggests that, like baseline PHQ-9 scores, responders have a higher ceiling from which to drop down, and an increase in values in later weeks indicates extremely low use in Weeks 1/2. More severe depression at baseline increases the likelihood of responding to treatment. 

Get normalization parameters
```{r}
norm_params_eda3 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_eda3 <- norm_params_eda3 |> 
  filter(terms %in% retained_vars_eda3$term)

# pivot wider
norm_params_retained_eda3 <- norm_params_retained_eda3 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_eda3, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```


### Fit final model: Engagement only, through Week 4

```{r}
rec <- build_recipe(d = d, config = best_config_eda4)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_eda4 <- fit_best_model(best_model = best_config_eda4, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_eda4 <- tidy(model_best_full_eda4)

model_tidy_eda4 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_eda4_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_eda4 <- model_tidy_eda4 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_eda4, digits = 6)
```

So, we see that:

People who spend more time in the app in week 2 (`total_time_wk2`) are *less* likely to be non-responders (i.e., are more likely to respond).

People whose time spent in the app increases over time (i.e., time spent in the app in Week 3 is higher than the average of time spent in-app across Weeks 1 & 2) are *more* likely to be non-responders (i.e., are less likely to respond). Given raw values of these variables across responder and non-responder groups (people who respond used the app more in earlier weeks), responders have a higher ceiling from which to drop down.

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

**Key Takeaways**: People who spend more time in the app early (Week 2) and whose time in-app does not increase in Week 3 are more likely to experience benefit. More severe depression at baseline increases the likelihood of responding to treatment. 

Get normalization parameters
```{r}
norm_params_eda4 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_eda4 <- norm_params_eda4 |> 
  filter(terms %in% retained_vars_eda4$term)

# pivot wider
norm_params_retained_eda4 <- norm_params_retained_eda4 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_eda4, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```

### Fit final model: Engagement + clinical, through Week 2

```{r}
rec <- build_recipe(d = d, config = best_config_phq2)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_phq2 <- fit_best_model(best_model = best_config_phq2, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_phq2 <- tidy(model_best_full_phq2)

model_tidy_phq2 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_phq2_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_phq2 <- model_tidy_phq2 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_phq2, digits = 6)
```

So, we see that:

People who spend more time in the app in Week 2 (`total_time_wk2` feature) are *less* likely to be non-responders (i.e., are more likely to respond). 

People who earn more badges in Week 1 (`badges_earned_wk1` feature) are *less* likely to be non-responders (i.e., are more likely to respond).

People who add more goals in Week 1 (`add_goal_wk1` feature) are *less* likely to be non-responders (i.e., are more likely to respond).

People who use the activity scheduling function more in Weeks 1 and 2 (`schedule_activity_*` features) are *less* likely to be non-responders (i.e., are more likely to respond).

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

People who have less negative change in PHQ-9 scores from baseline (i.e., whose scores *increase, stay the same, or only slightly decrease*; `phq9_change_bl` features) are *more* likely to be non-responders. These people are not experiencing early benefit from the app.

**Key Takeaways**: Engaging more, broadly (total time) and with BA-specific components, makes you more likely to respond to treatment. More severe depression at baseline increases the likelihood of responding to treatment. People who start to respond in the first two weeks are more likely to respond at 12 weeks.

Get normalization parameters
```{r}
norm_params_phq2 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_phq2 <- norm_params_phq2 |> 
  filter(terms %in% retained_vars_phq2$term)

# pivot wider
norm_params_retained_phq2 <- norm_params_retained_phq2 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_phq2, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```

### Fit final model: Engagement + clinical, through Week 3

```{r}
rec <- build_recipe(d = d, config = best_config_phq3)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_phq3 <- fit_best_model(best_model = best_config_phq3, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_phq3 <- tidy(model_best_full_phq3)

model_tidy_phq3 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_phq3_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_phq3 <- model_tidy_phq3 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_phq3, digits = 6)
```

So, we see that:

People who spend more time in the app in Week 2 (`total_time_wk2` feature) are *less* likely to be non-responders (i.e., are more likely to respond). People who spend more time in-app in Week 1 or Week 3 are *more* likely to be non-responders. 

People who have a higher average session time in Week 3 (`average_session_time_wk3` feature) are *less* likely to be non-responders (i.e., are more likely to respond).

People who have a higher session count across weeks (`session_count_wk*` features) are *less* likely to be non-responders (i.e., are more likely to respond). 

People whose time spent in the app increases over time (i.e., time spent in the app in Week 3 is higher than in Week 1 or than the average across Weeks 1 & 2) are *more* likely to be non-responders (i.e., are less likely to respond). Given raw values of these variables across responder and non-responder groups (people who respond used the app more in earlier weeks), responders have a higher ceiling from which to drop down.

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

People who have less negative change in PHQ-9 scores from baseline (i.e., whose scores *increase, stay the same, or only slightly decrease*; `phq9_change_bl` features) are *more* likely to be non-responders. These people are not experiencing early benefit from the app.

**Key Takeaways**: Engaging more broadly (total time, session count, and average session time) generally makes you more likely to respond to treatment. Greater change in total time in-app, which is likely indicative of low time in-app in early weeks, makes you less likely to respond to treatment. More severe depression at baseline increases the likelihood of responding to treatment. People who start to respond in the first three weeks are more likely to respond at 12 weeks.

Get normalization parameters
```{r}
norm_params_phq3 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_phq3 <- norm_params_phq3 |> 
  filter(terms %in% retained_vars_phq3$term)

# pivot wider
norm_params_retained_phq3 <- norm_params_retained_phq3 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_phq3, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```

### Fit final model: Engagement + clinical, through Week 4

```{r}
rec <- build_recipe(d = d, config = best_config_phq4)

rec_prepped_full <- rec |> 
  prep(training = d)

feat_all <- rec_prepped_full |> 
  bake(new_data = NULL)

penalty_weights <- c(0, rep(1, ncol(feat_all) - 2))

model_best_full_phq4 <- fit_best_model(best_model = best_config_phq4, 
                                       feat = feat_all, 
                                       ml_mode = ml_mode,
                                       algorithm = algorithm,
                                       penalty_weights = penalty_weights)
```

#### Model coefficients

**NOTE**: Coefficients are naturally inverted (i.e., positive class ["non-responder"] treated as first [vs. second] class). Here, we multiply coefficients by -1 to align the direction of coefficients with the rest of our analyses. Once flipped (i.e., as they appear below)...

A *positive coefficient* indicates that increases in the feature *increase* the likelihood of being a non-responder. 

A *negative coefficient* indicates that increases in the feature *decrease* the likelihood of being a non-responder (i.e., increase the likelihood of responding).

```{r}
model_tidy_phq4 <- tidy(model_best_full_phq4)

model_tidy_phq4 |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/model_best_phq4_tidy.csv")

```

Table of all "retained" features (i.e., features whose parameter estimates were non-zero; parameter estimates of 0 indicate removal from the model via LASSO selection). 

```{r}
retained_vars_phq4 <- model_tidy_phq4 |> 
  mutate(estimate = estimate * -1) |> 
  filter(abs(estimate) > 0) |> 
  select(-penalty) |> 
  arrange(desc(abs(estimate)))

knitr::kable(retained_vars_phq4, digits = 6)
```

So, we see that:

People who spend more time in the app across weeks (`total_time_wk*` features) are typically *less* likely to be non-responders (i.e., are more likely to respond). The exception is time in-app in Week 3, where more time in-app *increases* the likelihood of not responding.

People who have more discrete app sessions across weeks (`session_count_*` features) are *less* likely to be non-responders (i.e., are more likely to respond). 

People who have greater average session times in Week 3 (`average_session_time_wk3`) are *less* likely to be non-responders (i.e., are more likely to respond).

People who have greater change from early weeks to later weeks (`total_time_chg_*` features) are typically *more* likely to be non-responders (i.e., are less likely to respond). Given raw values of these variables across responder and non-responder groups (people who respond used the app more in earlier weeks), responders have a higher ceiling from which to drop down. The exception is change in time in-app from Week 4 from the previous average, where greater time in Week 4 (vs. average of Weeks 1-3) makes you *less* likely to be a non-responder (i.e., are more likely to respond).

People who have higher baseline PHQ scores (`y_base` feature) are *less* likely to be non-responders (i.e., are more likely to respond). These people have a higher ceiling from which to drop down.

People who have less negative change in PHQ-9 scores from baseline (i.e., whose scores *increase, stay the same, or only slightly decrease*; `phq9_change_bl` features) are *more* likely to be non-responders. These people are not experiencing early benefit from the app.

**Key Takeaways**: Engaging more broadly (total time, number of sessions, average session length) across weeks generally makes you more likely to respond to treatment. People More severe depression at baseline increases the likelihood of responding to treatment. Greater change in total time in-app in later weeks vs. earlier weeks, which is likely indicative of low time in-app in early weeks, generally makes you less likely to respond to treatment. More severe depression at baseline increases the likelihood of responding to treatment. People who start to respond in the first four weeks are more likely to respond at 12 weeks.

Get normalization parameters
```{r}
norm_params_phq4 <- tidy(rec_prepped_full, number = 2) # step 2 is normalization

# filter down to retained variables
norm_params_retained_phq4 <- norm_params_phq4 |> 
  filter(terms %in% retained_vars_phq4$term)

# pivot wider
norm_params_retained_phq4 <- norm_params_retained_phq4 |> 
  select(terms, statistic, value) |> 
  pivot_wider(names_from = statistic, values_from = value)

knitr::kable(norm_params_retained_phq4, digits = 6)

# will then need to do:
# ((feature value - mean) / sd ) * parameter estimate
```


## Model Calibration

To evaluate model calibration, we need to make predictions from each *final, best selected model configuration* for each observation when held-out. We will fit each best configuration on N-1 observations (341) and predicting the Nth (342nd), held-out observation. This method helps to keep each model as close to the final best model as possible (training set differs by only 1 observation). 

* Use only best configuration for each context (X6)
* Get predicted probabilities X4: raw, beta-calibrated, logistic-calibrated, isotonic-calibrated

### Get probabilities for held-out observations

Create function

```{r fcn_get_final_probs}
get_final_probs <- function(i_sub, best_config, d){
  
  # hold out single subject
  d_out <- d |> 
    filter(record_id == i_sub)
  
  d_in <- d |> 
    filter(record_id != i_sub)
  
  # prep recipe 
  rec <- build_recipe(d = d_in, config = best_config)
  rec_prepped <- rec |> 
    prep(training = d_in, strings_as_factors = FALSE)
  
  # bake feat_in and feat_out
  feat_in <- rec_prepped |> 
    bake(new_data = NULL)
  
  feat_out <- rec_prepped |> 
    bake(new_data = d_out)
  
  # set penalty_weights
  penalty_weights <- c(0, rep(1, ncol(feat_in) - 2))
  
  # fit model
  model_best <- fit_best_model(best_model = best_config, 
                               feat = feat_in, 
                               ml_mode = ml_mode,
                               algorithm = algorithm,
                               penalty_weights = penalty_weights)
  
  # raw (uncalibrated) predictions
  preds_prob <- predict(model_best, feat_out,
                        type = "prob")
  
  # fit calibration model
  set.seed(2468)
  cal_split <- d_in |> 
    initial_split(prop = 3/4, strata = y)
  d_cal_in <- training(cal_split) 
  d_cal_out <- testing(cal_split)
  
  rec_cal_prepped <- rec |> 
    prep(training = d_cal_in, strings_as_factors = FALSE)
  
  feat_cal_in <- rec_cal_prepped |> 
    bake(new_data = NULL) 
  
  feat_cal_out <- rec_cal_prepped |> 
    bake(new_data = d_cal_out) 
  
  penalty_weights_cal <- c(0, rep(1, ncol(feat_cal_in) - 2))
  
  model_cal <- fit_best_model(best_model = best_config, 
                              feat = feat_cal_in,
                              ml_mode = ml_mode,
                              algorithm = algorithm,
                              penalty_weights = penalty_weights)
  
  # beta calibration
  beta <- predict(model_cal, feat_cal_out,
                  type = "prob") |>
    mutate(truth = feat_cal_out$y) |>
    cal_estimate_beta(truth = truth,
                      estimate = dplyr::starts_with(".pred_"),
                      smooth = TRUE)
  preds_prob_beta <- preds_prob |>
    cal_apply(beta)
  
  # iso calibration
  iso <- predict(model_cal, feat_cal_out,
                 type = "prob") |>
    mutate(truth = feat_cal_out$y) |>
    cal_estimate_isotonic(truth = truth,
                          estimate = dplyr::starts_with(".pred_"))
  preds_prob_iso <- preds_prob |>
    cal_apply(iso)
  
  # logistic calibration
  logi <- predict(model_cal, feat_cal_out,
                  type = "prob") |>
    mutate(truth = feat_cal_out$y) |>
    cal_estimate_logistic(truth = truth,
                          estimate = dplyr::starts_with(".pred_"),
                          smooth = TRUE)
  preds_prob_logi <- preds_prob |>
    cal_apply(logi)
  
  # combine raw and calibrated probs
  probs <- tibble(record_id = d_out$record_id,
                  model = best_config$feature_set,
                  prob_raw = preds_prob[[".pred_non_responder"]],
                  prob_beta = preds_prob_beta[[".pred_non_responder"]],
                  prob_iso = preds_prob_iso[[".pred_non_responder"]],
                  prob_logi = preds_prob_logi[[".pred_non_responder"]]) 
}

```

Map over participants so that each is held-out once

```{r}
# engagement-only, week 2
probs_eda2 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_eda2, d)) |> 
  list_rbind()

# engagement-only, week 3
probs_eda3 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_eda3, d)) |> 
  list_rbind()

# engagement-only, week 4
probs_eda4 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_eda4, d)) |> 
  list_rbind()

# engagement + clinical, week 2
probs_phq2 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_phq2, d)) |> 
  list_rbind()

# engagement + clinical, week 3
probs_phq3 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_phq3, d)) |> 
  list_rbind()

# engagement + clinical, week 4
probs_phq4 <- d$record_id |> 
  map(\(i_sub) get_final_probs(i_sub, best_config = best_config_phq4, d)) |> 
  list_rbind()
```

### Evaluating model calibration

#### Engagement-only, through Week 2

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_eda2 <- d |> 
  select(record_id, y) |> 
  left_join(probs_eda2, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_eda2 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are close; isotonic-calibrated probabilities are far off.

Plot calibration
```{r}
# pivot to long format
d_plot_eda2 <- d_eda2 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_eda2 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_eda2 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_eda2$y,
                estimate = d_eda2$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_eda2$y,
                estimate = d_eda2$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_eda2$y,
                estimate = d_eda2$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_eda2$y,
                estimate = d_eda2$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

#### Engagement-only, through Week 3

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_eda3 <- d |> 
  select(record_id, y) |> 
  left_join(probs_eda3, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_eda3 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are next-closest; isotonic-calibrated probabilities are far off.

Plot calibration
```{r}
# pivot to long format
d_plot_eda3 <- d_eda3 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_eda3 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_eda3 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated, though not good for probabilities above 0.7.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_eda3$y,
                estimate = d_eda3$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_eda3$y,
                estimate = d_eda3$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_eda3$y,
                estimate = d_eda3$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_eda3$y,
                estimate = d_eda3$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

#### Engagement-only, through Week 4

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_eda4 <- d |> 
  select(record_id, y) |> 
  left_join(probs_eda4, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_eda4 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are next-closest; isotonic-calibrated probabilities are farther off.

Plot calibration
```{r}
# pivot to long format
d_plot_eda4 <- d_eda4 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_eda4 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_eda4 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated, though not great.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_eda4$y,
                estimate = d_eda4$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_eda4$y,
                estimate = d_eda4$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_eda4$y,
                estimate = d_eda4$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_eda4$y,
                estimate = d_eda4$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

#### Engagement + clinical, through Week 2

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_phq2 <- d |> 
  select(record_id, y) |> 
  left_join(probs_phq2, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_phq2 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are next-closest; isotonic-calibrated probabilities are far off.

Plot calibration
```{r}
# pivot to long format
d_plot_phq2 <- d_phq2 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_phq2 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_phq2 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated, though calibration drops off among highest probabilities.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_phq2$y,
                estimate = d_phq2$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_phq2$y,
                estimate = d_phq2$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_phq2$y,
                estimate = d_phq2$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_phq2$y,
                estimate = d_phq2$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

#### Engagement + clinical, through Week 3

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_phq3 <- d |> 
  select(record_id, y) |> 
  left_join(probs_phq3, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_phq3 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are next-closest; isotonic-calibrated probabilities are far off.

Plot calibration
```{r}
# pivot to long format
d_plot_phq3 <- d_phq3 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_phq3 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_phq3 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_phq3$y,
                estimate = d_phq3$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_phq3$y,
                estimate = d_phq3$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_phq3$y,
                estimate = d_phq3$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_phq3$y,
                estimate = d_phq3$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

#### Engagement + clinical, through Week 4

Compare mean non-response rate from RCT to predicted probabilities across calibrations
```{r}
d_phq4 <- d |> 
  select(record_id, y) |> 
  left_join(probs_phq4, by = "record_id") |> 
  mutate(y_num = if_else(y == "non_responder", 1, 0))

d_phq4 |> 
  summarize(mean_y = mean(y_num),
            mean_raw = mean(prob_raw),
            mean_beta = mean(prob_beta),
            mean_iso = mean(prob_iso),
            mean_logi = mean(prob_logi))
```
Raw probabilities match best. Beta- and logistic-calibrated probabilities are next-closest; isotonic-calibrated probabilities are far off.

Plot calibration
```{r}
# pivot to long format
d_plot_phq4 <- d_phq4 |> 
  pivot_longer(
    cols = c(prob_raw, prob_beta, prob_logi, prob_iso),
    names_to = "method",
    values_to = ".pred_non_responder"
  )

d_plot_phq4 |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = method)

d_plot_phq4 |> 
  cal_plot_windowed(truth = y,
                    estimate = .pred_non_responder,
                    .by = method)
```
Raw probabilities are the best calibrated.

Brier scores
```{r}
# raw probabilities
brier_class_vec(truth = d_phq4$y,
                estimate = d_phq4$prob_raw)

# beta calibrated probabilities
brier_class_vec(truth = d_phq4$y,
                estimate = d_phq4$prob_beta)

# logistic calibrated probabilities
brier_class_vec(truth = d_phq4$y,
                estimate = d_phq4$prob_logi)

# isotonic calibrated probabilities
brier_class_vec(truth = d_phq4$y,
                estimate = d_phq4$prob_iso)
```
Raw calibration has the lowest Brier score. In keeping with other methods above, beta and logistic are next-best followed by isotonic calibration, which has the highest Brier score.

### Make paneled figure

Set up plotting data (combined across)
```{r}
d_plot <- d_plot_eda2 |> 
  bind_rows(d_plot_eda3) |> 
  bind_rows(d_plot_eda4) |> 
  bind_rows(d_plot_phq2) |> 
  bind_rows(d_plot_phq3) |> 
  bind_rows(d_plot_phq4) |> 
  filter(method == "prob_raw") |> 
  select(record_id, y, model, .pred_non_responder) |> 
  mutate(data_type = if_else(str_detect(model, "phq"), "Eng+Clin", "Eng-Only"),
         week = str_sub(model, start = -1L, end = -1L)) |> 
  select(-model) |> 
  mutate(Model = str_c(data_type, ", Wk", week))
  
```

Plot calibration by model configuration
```{r}
d_plot |> 
  cal_plot_breaks(truth = y,
                  estimate = .pred_non_responder,
                  .by = Model) +
  labs(x = "Predicted Probability of Non-Response (bin mid-point)",
       y = "Observed Non-Response")
```


