---
title: "Clean & Prepare Data"
author: "Gaylen Fronk"
format: html
---

# Setup

Load libraries
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

## Read in data

```{r}
d <- read_csv("~/Desktop/musc/dahne_lab/moodivate/data_raw.csv", 
              show_col_types = FALSE)
```

## Prepare data 

### Create outcome & baseline variables

```{r}
d <- d |> 
  mutate(phq9_outcome_cat = if_else(phq9_change_bl_w12 > -5, 
                                   "NonResponder", 
                                   "Responder", 
                                   NA_character_)) |> 
  mutate(phq9_outcome_cat = factor(phq9_outcome_cat)) |> 
  rename(phq9_outcome_cont = phq9_change_bl_w12, 
         phq9_baseline = phq9_score_bl)
```

### Subset to participants with outcome data

```{r}
d <- d |> 
  filter(!is.na(phq9_outcome_cat))
```

### Clean up

Remove BDI variables & PHQ8 scores, remove predictors from after week 4, fix naming inconsistencies, remove "complete_activity" variables (decided not meaningful)

```{r}
d <- d |> 
  # standardize naming
  rename_with(~ str_replace(.x, "_wk", "_w")) |> 
  rename_with(~ str_replace(.x, "_w", "_wk")) |> 
  # remove unnecessary variables
  select(-starts_with("bdi"), 
         -ends_with(str_c("_wk", 5:12)),
         -starts_with("phq8_score"),
         -starts_with("phq8_change"),
         -starts_with("complete_activity")) |> 
  # fix scale for total time & average session time variables
  mutate(across(c(starts_with("total_time"), starts_with("average")),
                ~ .x / 60))
```

### LOCF for PHQ data

```{r}
d <- d |> 
  # wk1: no change from baseline because would carry baseline score forward
  mutate(phq9_change_bl_wk1 = if_else(is.na(phq9_change_bl_wk1),
                                     0,
                                     phq9_change_bl_wk1)) |> 
  # later weeks: carry change from baseline forward
  mutate(phq9_change_bl_wk2 = if_else(is.na(phq9_change_bl_wk2),
                                     phq9_change_bl_wk1, 
                                     phq9_change_bl_wk2)) |> 
  mutate(phq9_change_bl_wk3 = if_else(is.na(phq9_change_bl_wk3),
                                     phq9_change_bl_wk2, 
                                     phq9_change_bl_wk3)) |> 
  mutate(phq9_change_bl_wk4 = if_else(is.na(phq9_change_bl_wk4),
                                     phq9_change_bl_wk3, 
                                     phq9_change_bl_wk4))
```

### Create within subjects variables

```{r}
# Identify all variables ending with _wk#
all_week_vars <- d |> 
  select(contains("_wk") & !starts_with("phq9")) |> 
  names()

# Identify the "base names" (everything before "_wk#")
stem_vars <- unique(str_remove(all_week_vars, "_wk\\d+$"))

for (stem in stem_vars) {
  
  later_week_vars <- str_c(stem, "_wk", 2:4)
  
  # 1) Change from week 1
  d[str_c(stem, "_chg_wk1_wk", 2:4)] <-
    d[later_week_vars] - d[[str_c(stem, "_wk1")]]
  
  # 2) Change from average of all previous weeks
  d[str_c(stem, "_chg_from_avg_wk", 3:4)] <-
    map_dfc(3:4, function(week_num) {
      prev_cols <- str_c(stem, "_wk", 1:(week_num - 1))
      d[[str_c(stem, "_wk", week_num)]] -
        rowMeans(d[prev_cols], na.rm = TRUE)
    })
  
  # 3) Change from previous week
  d[str_c(stem, "_chg_from_prev_wk", 3:4)] <-
    map_dfc(3:4, function(week_num) {
      prev_cols <- str_c(stem, "_wk", 1:(week_num - 1))
      d[[str_c(stem, "_wk", week_num)]] -
        d[[str_c(stem, "_wk", week_num - 1)]]
    })
}
```

## Glimpse

```{r}
glimpse(d)
```

## Write out cleaned data file

```{r}
d |> 
  write_csv("~/Desktop/musc/dahne_lab/moodivate/data_clean.csv")
```

## EDA Table

```{r}
library(gtsummary)
tblsum_object <- d |>
  tbl_summary(by = phq9_outcome_cat,
              include = !c(record_id),
              digits = all_continuous() ~ 2
  ) |>
  add_overall() |>
  modify_header(label ~ "Predictor") |>
  modify_spanning_header(c("stat_1", "stat_2") ~ "Response Category (PHQ9)") |>
  add_p(test.args = c("mood_days_wk4",
                      "mood_days_wk2",
                      "mood_days_chg_from_prev_wk3") ~ list(
                         simulate.p.value = TRUE
                       ),
        pvalue_fun = label_style_pvalue(digits = 3))
```

Results of basic EDA:

p-values < 0.1 & > 0.05:
session_count_wk3, average_session_time_wk3, completed_activities_wk1, mood_days_wk1, add_goal_chg_wk1_wk3/4, add_goal_chg_from_avg_wk3/4, badges_earned_chg_wk1_wk4, badges_earned_chg_from_avg_wk4, phq8_comp_chg_wk1_wk4

p-values < 0.05:
session_count_wk1/2/4, total_time_wk1/2/3/4, schedule_activity_wk1/2/3/4, scheduled_activities_wk1/2/3/4, completed_activities_wk3/4, add_goal_wk1, badges_earned_wk1/3, total_time_chg_wk1_wk3/4, total_time_chg_from_avg_wk3/4, schedule_activity_chg_from_prev_wk3

session_count_wk1
session_count_wk2
total_time_wk1
total_time_wk2
schedule_activity_wk1
schedule_activity_wk2
scheduled_activities_wk1
scheduled_activities_wk2
add_goal_wk1
badges_earned_wk1